### 2020-06-19 2020/phd_midterm_report/report.tex
rewriting

\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted by positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions
.
\section*{Planning for the next 18 months}

\begin{itemize}
\item Complete work on residual adapters and submission to WMT 2020 at the end of July 2020.
\item Complete system submission to Machine Translation Robustness task of WMT 2020 at the end of July 2020.
\item Complete work on contextualized Machine Translation with Systran's team at the end of July 2020.
\item Complete  work on Multi-source Adaptation between August - December 2020.
\item Complete work on BPE-vocabulary's transfer learning effect between January and March 2021.
\item Finalize publications, write PhD memoire between March and August 2021.
\item Defend PhD September 2021.
\end{itemize}

>>>>

\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted to positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions. 
.
\section*{Planning for the next 18 months}

\begin{itemize}
\item Complete work on residual adapters and submission to WMT 2020 at the end of July 2020.
\item Complete system submission to Machine Translation Robustness task of WMT 2020 at the end of July 2020.
\item Complete work on contextualized Machine Translation with Systran's team at the end of July 2020.
\item Complete  work on Multi-source Adaptation between August - December 2020.
\item Complete work on BPE-vocabulary's transfer learning effect between January and March 2021.
\item Finalize publications, write PhD memoire between April and September 2021.
\item Defend PhD October 2021.
\end{itemize}
